---
title: "core_periphery"
author: "Author"
date: "2025-08-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file splits each year's global trade network into core and periphery and adds a binary variable for core-periphery to the attributeYEAR datasets. 

Steps: 
1. It reads the edgelist for total trade. Then for every time period it goes through the following steps,
   a. Creates a weighted directed igraph objects and adds vertex attributes from attribute data
   b. Splits core-periphery on the igraph object
   c. Makes a dataframe of the core-periphery output and merges it with the attribute data of that year 
   d. Removes the unrelevant columns and replaces the attribute csv file in the `cleaned` subfolder with the merged data

```{r}
library(igraph)
library(ITNr)
```


```{r}
t <- read.csv("../data/cleaned/trade_edgelist.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
```
# 2000
```{r}
y0 <- "X2000"   
t_y0 <- t[, c("iso_o", "iso_d", y0)]
# Filtering out edges with zero trade
t_y0 <- subset(t_y0, t_y0[[y0]] > 0)
att2000 <- read.csv("../data/cleaned/attribute2000.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot00 <- graph_from_data_frame(d = t_y0, directed = TRUE)
E(tot00)$weight <- t_y0[[y0]]
is_directed(tot00) 
length(E(tot00)) == length(E(tot00)$weight)
length(unique(V(tot00)$name)) == gorder(tot00)  
is.character(V(tot00)$name) 
any(is.na(E(tot00)$weight))      
any(!is.finite(E(tot00)$weight))
length(unique(V(tot00)$name))
```

```{r}
attify <- function(n_net, attr_df){
  V(n_net)$iso_o <- V(n_net)$name
  idx <- match(V(n_net)$name, attr_df$iso_o)
  V(n_net)$country <- attr_df$country_x[idx]
  return(n_net)
}

tot00 <- attify(tot00, att2000)
vertex_attr_names(tot00)
```

```{r}
#vcount(tot00)
#nrow(att2000)
```

```{r}
summary(tot00)
length(unique(V(tot00)$name)) == gorder(tot00) 
is.character(V(tot00)$name) 
length(unique(att2000$iso_o)) == length(unique(V(tot00)$name))
V(tot00)$name

ITNcp00 <-core_periphery_weighted(tot00,"directed")
# This is a list of three. The second element is the dataframe containing the results.
class(ITNcp00)

length(ITNcp00)
class(ITNcp00[[1]])
class(ITNcp00[[2]])
ITNcp00[[2]]

#Making sure the class, the string lengths and the values of the columns to merge the dataframes are same
cp00 <- ITNcp00[[2]]
class(cp00$id)
class(att2000$iso_o)
unique(nchar(cp00$id))
unique(nchar(att2000$iso_o))
head(cp00$id)
head(att2000$iso_o)
```

```{r}
#merged00 <- merge(cp00, att2000, by.x = "id", by.y = "iso_o", all.x = TRUE)
#merged00 <- left_join(cp00, att2000, by = "id")
#merged00 <- subset(merged00, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, X, sigma_all.y, RANK.y, all_cp.y ))
# renaming 
#merged00 <- merged00 %>% rename(iso_o = id)
merged00 <- merged00 %>% rename(sigma_cp = sigma_all.x)
merged00 <- merged00 %>% rename(rank_cp = RANK.x)
merged00 <- merged00 %>% rename(cp = all_cp.x)
merged00 <- merged00 %>% rename(country = country_x)
```

```{r}
colnames(merged00)
```

# 2001
```{r}
y1 <- "X2001"   
t_y1 <- t[, c("iso_o", "iso_d", y1)]
t_y1 <- subset(t_y1, t_y1[[y1]] > 0)
att2001 <- read.csv("../data/cleaned/attribute2001.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot01 <- graph_from_data_frame(d = t_y1, directed = TRUE)
E(tot01)$weight <- t_y1[[y1]]
is_directed(tot01) 
length(E(tot01)) == length(E(tot01)$weight)
length(unique(V(tot01)$name)) == gorder(tot01)  
is.character(V(tot01)$name) 
any(is.na(E(tot01)$weight))      
any(!is.finite(E(tot01)$weight))
length(unique(V(tot01)$name))

tot01 <- attify(tot01, att2001)
vertex_attr_names(tot01)
```

```{r}

length(unique(V(tot01)$name)) == gorder(tot01) 
is.character(V(tot01)$name) 
length(unique(att2001$iso_o)) == length(unique(V(tot01)$name))

ITNcp01 <-core_periphery_weighted(tot01,"directed")
class(ITNcp01[[2]])
cp01 <- ITNcp01[[2]]

#Making sure the class, the string lengths and the values of the columns to merge the dataframes are same
class(cp01$id)
class(att2001$iso_o)
unique(nchar(cp01$id))
unique(nchar(att2001$iso_o))
head(cp01$id)
head(att2001$iso_o)
```

```{r}
merged01 <- merge(cp01, att2001, by.x = "id", by.y = "iso_o", all.x = TRUE)
#merged01 <- left_join(cp01, att2001, by = "id")
merged01 <- subset(merged01, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged01 <- merged01 %>% rename(iso_o = id)
merged01 <- merged01 %>% rename(sigma_cp = sigma_all)
merged01 <- merged01 %>% rename(rank_cp = RANK)
merged01 <- merged01 %>% rename(cp = all_cp)
merged01 <- merged01 %>% rename(country = country_x)
```

```{r}
colnames(merged01)
```
# 2002
```{r}
y2 <- "X2002"   
t_y2 <- t[, c("iso_o", "iso_d", y2)]
t_y2 <- subset(t_y2, t_y2[[y2]] > 0)
att2002 <- read.csv("../data/cleaned/attribute2002.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot02 <- graph_from_data_frame(d = t_y2, directed = TRUE)
E(tot02)$weight <- t_y2[[y2]]
is_directed(tot02) 
length(E(tot02)) == length(E(tot02)$weight)
length(unique(V(tot02)$name)) == gorder(tot02)  
is.character(V(tot02)$name) 
any(is.na(E(tot02)$weight))      
any(!is.finite(E(tot02)$weight))
length(unique(V(tot02)$name))

tot02 <- attify(tot02, att2002)
vertex_attr_names(tot02)
```

```{r}
length(unique(V(tot02)$name)) == gorder(tot02) 
is.character(V(tot02)$name) 
length(unique(att2002$iso_o)) == length(unique(V(tot02)$name))

ITNcp02 <-core_periphery_weighted(tot02,"directed")
class(ITNcp02[[2]])
cp02 <- ITNcp02[[2]]
```
```{r}
merged02 <- merge(cp02, att2002, by.x = "id", by.y = "iso_o", all.x = TRUE)
#merged01 <- left_join(cp01, att2001, by = "id")
merged02 <- subset(merged02, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged02 <- merged02 %>% rename(iso_o = id)
merged02 <- merged02 %>% rename(sigma_cp = sigma_all)
merged02 <- merged02 %>% rename(rank_cp = RANK)
merged02 <- merged02 %>% rename(cp = all_cp)
merged02 <- merged02 %>% rename(country = country_x)
```

# 2003
```{r}
y3 <- "X2003"   
t_y3 <- t[, c("iso_o", "iso_d", y3)]
t_y3 <- subset(t_y3, t_y3[[y3]] > 0)
att2003 <- read.csv("../data/cleaned/attribute2003.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot03 <- graph_from_data_frame(d = t_y3, directed = TRUE)
E(tot03)$weight <- t_y3[[y3]]
is_directed(tot03) 
length(E(tot03)) == length(E(tot03)$weight)
length(unique(V(tot03)$name)) == gorder(tot03)  
is.character(V(tot03)$name) 
any(is.na(E(tot03)$weight))      
any(!is.finite(E(tot03)$weight))
length(unique(V(tot03)$name))

tot03 <- attify(tot03, att2003)
vertex_attr_names(tot03)
```


```{r}
length(unique(V(tot03)$name)) == gorder(tot03) 
is.character(V(tot03)$name) 
length(unique(att2003$iso_o)) == length(unique(V(tot03)$name))
ITNcp03 <-core_periphery_weighted(tot03,"directed")
class(ITNcp03[[2]])
cp03 <- ITNcp03[[2]]
```
```{r}
merged03 <- merge(cp03, att2003, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged03 <- subset(merged03, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged03 <- merged03 %>% rename(iso_o = id)
merged03 <- merged03 %>% rename(sigma_cp = sigma_all)
merged03 <- merged03 %>% rename(rank_cp = RANK)
merged03 <- merged03 %>% rename(cp = all_cp)
merged03 <- merged03 %>% rename(country = country_x)
```



# 2004
```{r}
y4 <- "X2004"   
t_y4 <- t[, c("iso_o", "iso_d", y4)]
t_y4 <- subset(t_y4, t_y4[[y4]] > 0)
att2004 <- read.csv("../data/cleaned/attribute2004.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot04 <- graph_from_data_frame(d = t_y4, directed = TRUE)
E(tot04)$weight <- t_y4[[y4]]
is_directed(tot04) 
length(E(tot04)) == length(E(tot04)$weight)
length(unique(V(tot04)$name)) == gorder(tot04) 
is.character(V(tot04)$name) 
any(is.na(E(tot04)$weight))      
any(!is.finite(E(tot04)$weight)) 
length(unique(V(tot04)$name))
tot04 <- attify(tot04, att2004)
vertex_attr_names(tot04)
```
```{r}
length(unique(V(tot04)$name)) == gorder(tot04) 
is.character(V(tot04)$name) 
length(unique(att2004$iso_o)) == length(unique(V(tot04)$name))
ITNcp04 <-core_periphery_weighted(tot04,"directed")
class(ITNcp04[[2]])
cp04 <- ITNcp04[[2]]
```
```{r}
merged04 <- merge(cp04, att2004, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged04 <- subset(merged04, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged04 <- merged04 %>% rename(iso_o = id)
merged04 <- merged04 %>% rename(sigma_cp = sigma_all)
merged04 <- merged04 %>% rename(rank_cp = RANK)
merged04 <- merged04 %>% rename(cp = all_cp)
merged04 <- merged04 %>% rename(country = country_x)
```

# 2005
```{r}
y5 <- "X2005"   
t_y5 <- t[, c("iso_o", "iso_d", y5)]
t_y5 <- subset(t_y5, t_y5[[y5]] > 0)
att2005 <- read.csv("../data/cleaned/attribute2005.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot05 <- graph_from_data_frame(d = t_y5, directed = TRUE)
E(tot05)$weight <- t_y5[[y5]]
is_directed(tot05) 
length(E(tot05)) == length(E(tot05)$weight)
length(unique(V(tot05)$name)) == gorder(tot05)  
is.character(V(tot05)$name) 
any(is.na(E(tot05)$weight))      
any(!is.finite(E(tot05)$weight)) 
length(unique(V(tot05)$name))
tot05 <- attify(tot05, att2005)
vertex_attr_names(tot05)
```

```{r}
length(unique(V(tot05)$name)) == gorder(tot05) 
is.character(V(tot05)$name) 
length(unique(att2005$iso_o)) == length(unique(V(tot05)$name))
ITNcp05 <-core_periphery_weighted(tot05,"directed")
class(ITNcp05[[2]])
cp05 <- ITNcp05[[2]]
```

```{r}
merged05 <- merge(cp05, att2005, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged05 <- subset(merged05, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged05 <- merged05 %>% rename(iso_o = id)
merged05 <- merged05 %>% rename(sigma_cp = sigma_all)
merged05 <- merged05 %>% rename(rank_cp = RANK)
merged05 <- merged05 %>% rename(cp = all_cp)
merged05 <- merged05 %>% rename(country = country_x)
```

# 2006
```{r}
y6 <- "X2006"   
t_y6 <- t[, c("iso_o", "iso_d", y6)]
t_y6 <- subset(t_y6, t_y6[[y6]] > 0)
att2006 <- read.csv("../data/cleaned/attribute2006.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot06 <- graph_from_data_frame(d = t_y6, directed = TRUE)
E(tot06)$weight <- t_y6[[y6]]
is_directed(tot06) 
length(E(tot06)) == length(E(tot06)$weight)
length(unique(V(tot06)$name)) == gorder(tot06)  
is.character(V(tot06)$name) 
any(is.na(E(tot06)$weight))    
any(!is.finite(E(tot06)$weight))
length(unique(V(tot06)$name))
tot06 <- attify(tot06, att2006)
vertex_attr_names(tot06)
```

```{r}
length(unique(V(tot06)$name)) == gorder(tot06) 
is.character(V(tot06)$name) 
length(unique(att2006$iso_o)) == length(unique(V(tot06)$name))
ITNcp06 <-core_periphery_weighted(tot06,"directed")
class(ITNcp06[[2]])
cp06 <- ITNcp06[[2]]
```

```{r}
merged06 <- merge(cp06, att2006, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged06 <- subset(merged06, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged06 <- merged06 %>% rename(iso_o = id)
merged06 <- merged06 %>% rename(sigma_cp = sigma_all)
merged06 <- merged06 %>% rename(rank_cp = RANK)
merged06 <- merged06 %>% rename(cp = all_cp)
merged06 <- merged06 %>% rename(country = country_x)
```

# 2007
```{r}
y7 <- "X2007"   
t_y7 <- t[, c("iso_o", "iso_d", y7)]
t_y7 <- subset(t_y7, t_y7[[y7]] > 0)
att2007 <- read.csv("../data/cleaned/attribute2007.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot07 <- graph_from_data_frame(d = t_y7, directed = TRUE)
E(tot07)$weight <- t_y7[[y7]]
is_directed(tot07) 
length(E(tot07)) == length(E(tot07)$weight)
length(unique(V(tot07)$name)) == gorder(tot07)  
is.character(V(tot07)$name) 
any(is.na(E(tot07)$weight))      
any(!is.finite(E(tot07)$weight)) 
length(unique(V(tot07)$name))
tot07 <- attify(tot07, att2007)
vertex_attr_names(tot07)
```
```{r}
length(unique(V(tot07)$name)) == gorder(tot07) 
is.character(V(tot07)$name) 
length(unique(att2007$iso_o)) == length(unique(V(tot07)$name))
ITNcp07 <-core_periphery_weighted(tot07,"directed")
class(ITNcp07[[2]])
cp07 <- ITNcp07[[2]]
```
```{r}
merged07 <- merge(cp07, att2007, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged07 <- subset(merged07, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged07 <- merged07 %>% rename(iso_o = id)
merged07 <- merged07 %>% rename(sigma_cp = sigma_all)
merged07 <- merged07 %>% rename(rank_cp = RANK)
merged07 <- merged07 %>% rename(cp = all_cp)
merged07 <- merged07 %>% rename(country = country_x)
```


# 2008
```{r}
y8 <- "X2008"   
t_y8 <- t[, c("iso_o", "iso_d", y8)]
t_y8 <- subset(t_y8, t_y8[[y8]] > 0)
att2008 <- read.csv("../data/cleaned/attribute2008.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot08 <- graph_from_data_frame(d = t_y8, directed = TRUE)
E(tot08)$weight <- t_y8[[y8]]
is_directed(tot08) 
length(E(tot08)) == length(E(tot08)$weight)
length(unique(V(tot08)$name)) == gorder(tot08)  
is.character(V(tot08)$name) 
any(is.na(E(tot08)$weight))      
any(!is.finite(E(tot08)$weight)) 
length(unique(V(tot08)$name))
tot08 <- attify(tot08, att2008)
vertex_attr_names(tot08)
```
```{r}
length(unique(V(tot08)$name)) == gorder(tot08) 
is.character(V(tot08)$name) 
length(unique(att2008$iso_o)) == length(unique(V(tot08)$name))
ITNcp08 <-core_periphery_weighted(tot08,"directed")
class(ITNcp08[[2]])
cp08 <- ITNcp08[[2]]
```
```{r}
merged08 <- merge(cp08, att2008, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged08 <- subset(merged08, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged08 <- merged08 %>% rename(iso_o = id)
merged08 <- merged08 %>% rename(sigma_cp = sigma_all)
merged08 <- merged08 %>% rename(rank_cp = RANK)
merged08 <- merged08 %>% rename(cp = all_cp)
merged08 <- merged08 %>% rename(country = country_x)
```

# 2009
```{r}
y9 <- "X2009"   
t_y9 <- t[, c("iso_o", "iso_d", y9)]
t_y9 <- subset(t_y9, t_y9[[y9]] > 0)
att2009 <- read.csv("../data/cleaned/attribute2009.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot09 <- graph_from_data_frame(d = t_y9, directed = TRUE)
E(tot09)$weight <- t_y9[[y9]]
is_directed(tot09) 
length(E(tot09)) == length(E(tot09)$weight)
length(unique(V(tot09)$name)) == gorder(tot09)  
is.character(V(tot09)$name) 
any(is.na(E(tot09)$weight))      
any(!is.finite(E(tot09)$weight)) 
length(unique(V(tot09)$name))
tot09 <- attify(tot09, att2009)
vertex_attr_names(tot09)
```
```{r}
length(unique(V(tot09)$name)) == gorder(tot09) 
is.character(V(tot09)$name) 
length(unique(att2009$iso_o)) == length(unique(V(tot09)$name))
ITNcp09 <-core_periphery_weighted(tot09,"directed")
class(ITNcp09[[2]])
cp09 <- ITNcp09[[2]]
```
```{r}
merged09 <- merge(cp09, att2009, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged09 <- subset(merged09, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged09 <- merged09 %>% rename(iso_o = id)
merged09 <- merged09 %>% rename(sigma_cp = sigma_all)
merged09 <- merged09 %>% rename(rank_cp = RANK)
merged09 <- merged09 %>% rename(cp = all_cp)
merged09 <- merged09 %>% rename(country = country_x)
```

# 2010
```{r}
y10 <- "X2010"   
t_y10 <- t[, c("iso_o", "iso_d", y10)]
t_y10 <- subset(t_y10, t_y10[[y10]] > 0)
att2010 <- read.csv("../data/cleaned/attribute2010.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot10 <- graph_from_data_frame(d = t_y10, directed = TRUE)
E(tot10)$weight <- t_y10[[y10]]
is_directed(tot10) 
length(E(tot10)) == length(E(tot10)$weight)
length(unique(V(tot10)$name)) == gorder(tot10)  
is.character(V(tot10)$name) 
any(is.na(E(tot10)$weight))      
any(!is.finite(E(tot10)$weight)) 
length(unique(V(tot10)$name))
tot10 <- attify(tot10, att2010)
vertex_attr_names(tot10)
```
```{r}
length(unique(V(tot10)$name)) == gorder(tot10) 
is.character(V(tot10)$name) 
length(unique(att2010$iso_o)) == length(unique(V(tot10)$name))
ITNcp10 <-core_periphery_weighted(tot10,"directed")
class(ITNcp10[[2]])
cp10 <- ITNcp10[[2]]
```

```{r}
merged10 <- merge(cp10, att2010, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged10 <- subset(merged10, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged10 <- merged10 %>% rename(iso_o = id)
merged10 <- merged10 %>% rename(sigma_cp = sigma_all)
merged10 <- merged10 %>% rename(rank_cp = RANK)
merged10 <- merged10 %>% rename(cp = all_cp)
merged10 <- merged10 %>% rename(country = country_x)
```

# 2011
```{r}
y11 <- "X2011"   
t_y11 <- t[, c("iso_o", "iso_d", y11)]
t_y11 <- subset(t_y11, t_y11[[y11]] > 0)
att2011 <- read.csv("../data/cleaned/attribute2011.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot11 <- graph_from_data_frame(d = t_y11, directed = TRUE)
E(tot11)$weight <- t_y11[[y11]]
is_directed(tot11) 
length(E(tot11)) == length(E(tot11)$weight)
length(unique(V(tot11)$name)) == gorder(tot11)  
is.character(V(tot11)$name) 
any(is.na(E(tot11)$weight))      
any(!is.finite(E(tot11)$weight))
length(unique(V(tot11)$name))
tot11 <- attify(tot11, att2011)
vertex_attr_names(tot11)
```
```{r}
length(unique(V(tot11)$name)) == gorder(tot11) 
is.character(V(tot11)$name) 
length(unique(att2011$iso_o)) == length(unique(V(tot11)$name))
ITNcp11 <-core_periphery_weighted(tot11,"directed")
class(ITNcp11[[2]])
cp11 <- ITNcp11[[2]]
```
```{r}
merged11 <- merge(cp11, att2011, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged11 <- subset(merged11, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged11 <- merged11 %>% rename(iso_o = id)
merged11 <- merged11 %>% rename(sigma_cp = sigma_all)
merged11 <- merged11 %>% rename(rank_cp = RANK)
merged11 <- merged11 %>% rename(cp = all_cp)
merged11 <- merged11 %>% rename(country = country_x)
```

# 2012
```{r}
y12 <- "X2012"   
t_y12 <- t[, c("iso_o", "iso_d", y12)]
t_y12 <- subset(t_y12, t_y12[[y12]] > 0)
att2012 <- read.csv("../data/cleaned/attribute2012.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot12 <- graph_from_data_frame(d = t_y12, directed = TRUE)
E(tot12)$weight <- t_y12[[y12]]
is_directed(tot12) 
length(E(tot12)) == length(E(tot12)$weight)
length(unique(V(tot12)$name)) == gorder(tot12)  
is.character(V(tot12)$name) 
any(is.na(E(tot12)$weight))      
any(!is.finite(E(tot12)$weight)) 
length(unique(V(tot12)$name))
tot12 <- attify(tot12, att2012)
vertex_attr_names(tot12)
```
```{r}
length(unique(V(tot12)$name)) == gorder(tot12) 
is.character(V(tot12)$name) 
length(unique(att2012$iso_o)) == length(unique(V(tot12)$name))
ITNcp12 <-core_periphery_weighted(tot12,"directed")
class(ITNcp12[[2]])
cp12 <- ITNcp12[[2]]
```
```{r}
merged12 <- merge(cp12, att2012, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged12 <- subset(merged12, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged12 <- merged12 %>% rename(iso_o = id)
merged12 <- merged12 %>% rename(sigma_cp = sigma_all)
merged12 <- merged12 %>% rename(rank_cp = RANK)
merged12 <- merged12 %>% rename(cp = all_cp)
merged12 <- merged12 %>% rename(country = country_x)
```

# 2013
```{r}
y13 <- "X2013"   
t_y13 <- t[, c("iso_o", "iso_d", y13)]
t_y13 <- subset(t_y13, t_y13[[y13]] > 0)
att2013 <- read.csv("../data/cleaned/attribute2013.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot13 <- graph_from_data_frame(d = t_y13, directed = TRUE)
E(tot13)$weight <- t_y13[[y13]]
is_directed(tot13) 
length(E(tot13)) == length(E(tot13)$weight)
length(unique(V(tot13)$name)) == gorder(tot13)  
is.character(V(tot13)$name) 
any(is.na(E(tot13)$weight))      
any(!is.finite(E(tot13)$weight)) 
length(unique(V(tot13)$name))
tot13 <- attify(tot13, att2013)
vertex_attr_names(tot13)
```
```{r}
length(unique(V(tot13)$name)) == gorder(tot13) 
is.character(V(tot13)$name) 
length(unique(att2013$iso_o)) == length(unique(V(tot13)$name))
ITNcp13 <-core_periphery_weighted(tot13,"directed")
class(ITNcp13[[2]])
cp13 <- ITNcp13[[2]]
```

```{r}
merged13 <- merge(cp13, att2013, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged13 <- subset(merged13, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged13 <- merged13 %>% rename(iso_o = id)
merged13 <- merged13 %>% rename(sigma_cp = sigma_all)
merged13 <- merged13 %>% rename(rank_cp = RANK)
merged13 <- merged13 %>% rename(cp = all_cp)
merged13 <- merged13 %>% rename(country = country_x)
```

# 2014
```{r}
y14 <- "X2014"   
t_y14 <- t[, c("iso_o", "iso_d", y14)]
t_y14 <- subset(t_y14, t_y14[[y14]] > 0)
att2014 <- read.csv("../data/cleaned/attribute2014.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot14 <- graph_from_data_frame(d = t_y14, directed = TRUE)
E(tot14)$weight <- t_y14[[y14]]
is_directed(tot14) 
length(E(tot14)) == length(E(tot14)$weight)
length(unique(V(tot14)$name)) == gorder(tot14)  
is.character(V(tot14)$name) 
any(is.na(E(tot14)$weight))      
any(!is.finite(E(tot14)$weight)) 
length(unique(V(tot14)$name))
tot14 <- attify(tot14, att2014)
vertex_attr_names(tot14)
```

```{r}
length(unique(V(tot14)$name)) == gorder(tot14) 
is.character(V(tot14)$name) 
length(unique(att2014$iso_o)) == length(unique(V(tot14)$name))
ITNcp14 <-core_periphery_weighted(tot14,"directed")
class(ITNcp14[[2]])
cp14 <- ITNcp14[[2]]
```

```{r}
merged14 <- merge(cp14, att2014, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged14 <- subset(merged14, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged14 <- merged14 %>% rename(iso_o = id)
merged14 <- merged14 %>% rename(sigma_cp = sigma_all)
merged14 <- merged14 %>% rename(rank_cp = RANK)
merged14 <- merged14 %>% rename(cp = all_cp)
merged14 <- merged14 %>% rename(country = country_x)
```


# 2015
```{r}
y15 <- "X2015"   
t_y15 <- t[, c("iso_o", "iso_d", y15)]
t_y15 <- subset(t_y15, t_y15[[y15]] > 0)
att2015 <- read.csv("../data/cleaned/attribute2015.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot15 <- graph_from_data_frame(d = t_y15, directed = TRUE)
E(tot15)$weight <- t_y15[[y15]]
is_directed(tot15) 
length(E(tot15)) == length(E(tot15)$weight)
length(unique(V(tot15)$name)) == gorder(tot15)  
is.character(V(tot15)$name) 
any(is.na(E(tot15)$weight))      
any(!is.finite(E(tot15)$weight)) 
length(unique(V(tot15)$name))
tot15 <- attify(tot15, att2015)
vertex_attr_names(tot15)
```
```{r}
length(unique(V(tot15)$name)) == gorder(tot15) 
is.character(V(tot15)$name) 
length(unique(att2015$iso_o)) == length(unique(V(tot15)$name))
ITNcp15 <-core_periphery_weighted(tot15,"directed")
class(ITNcp15[[2]])
cp15 <- ITNcp15[[2]]
```
```{r}
merged15 <- merge(cp15, att2015, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged15 <- subset(merged15, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged15 <- merged15 %>% rename(iso_o = id)
merged15 <- merged15 %>% rename(sigma_cp = sigma_all)
merged15 <- merged15 %>% rename(rank_cp = RANK)
merged15 <- merged15 %>% rename(cp = all_cp)
merged15 <- merged15 %>% rename(country = country_x)
```


# 2016
```{r}
y16 <- "X2016"   
t_y16 <- t[, c("iso_o", "iso_d", y16)]
t_y16 <- subset(t_y16, t_y16[[y16]] > 0)
att2016 <- read.csv("../data/cleaned/attribute2016.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot16 <- graph_from_data_frame(d = t_y16, directed = TRUE)
E(tot16)$weight <- t_y16[[y16]]
is_directed(tot16) 
length(E(tot16)) == length(E(tot16)$weight)
length(unique(V(tot16)$name)) == gorder(tot16)  
is.character(V(tot16)$name) 
any(is.na(E(tot16)$weight))      
any(!is.finite(E(tot16)$weight)) 
length(unique(V(tot16)$name))
tot16 <- attify(tot16, att2016)
vertex_attr_names(tot16)
```
```{r}
length(unique(V(tot16)$name)) == gorder(tot16) 
is.character(V(tot16)$name) 
length(unique(att2016$iso_o)) == length(unique(V(tot16)$name))
ITNcp16 <-core_periphery_weighted(tot16,"directed")
class(ITNcp16[[2]])
cp16 <- ITNcp16[[2]]
```

```{r}
merged16 <- merge(cp16, att2016, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged16 <- subset(merged16, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged16 <- merged16 %>% rename(iso_o = id)
merged16 <- merged16 %>% rename(sigma_cp = sigma_all)
merged16 <- merged16 %>% rename(rank_cp = RANK)
merged16 <- merged16 %>% rename(cp = all_cp)
merged16 <- merged16 %>% rename(country = country_x)
```

# 2017
```{r}
y17 <- "X2017"   
t_y17 <- t[, c("iso_o", "iso_d", y17)]
t_y17 <- subset(t_y17, t_y17[[y17]] > 0)
att2017 <- read.csv("../data/cleaned/attribute2017.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot17 <- graph_from_data_frame(d = t_y17, directed = TRUE)
E(tot17)$weight <- t_y17[[y17]]
is_directed(tot17) 
length(E(tot17)) == length(E(tot17)$weight)
length(unique(V(tot17)$name)) == gorder(tot17)  
is.character(V(tot17)$name) 
any(is.na(E(tot17)$weight))     
any(!is.finite(E(tot17)$weight))
length(unique(V(tot17)$name))
tot17 <- attify(tot17, att2017)
vertex_attr_names(tot17)
```

```{r}
length(unique(V(tot17)$name)) == gorder(tot17) 
is.character(V(tot17)$name) 
length(unique(att2017$iso_o)) == length(unique(V(tot17)$name))
ITNcp17 <-core_periphery_weighted(tot17,"directed")
class(ITNcp17[[2]])
cp17 <- ITNcp17[[2]]
```

```{r}
merged17 <- merge(cp17, att2017, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged17 <- subset(merged17, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged17 <- merged17 %>% rename(iso_o = id)
merged17 <- merged17 %>% rename(sigma_cp = sigma_all)
merged17 <- merged17 %>% rename(rank_cp = RANK)
merged17 <- merged17 %>% rename(cp = all_cp)
merged17 <- merged17 %>% rename(country = country_x)
```

#2018
```{r}
y18 <- "X2018"   
t_y18 <- t[, c("iso_o", "iso_d", y18)]
t_y18 <- subset(t_y18, t_y18[[y18]] > 0)
att2018 <- read.csv("../data/cleaned/attribute2018.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot18 <- graph_from_data_frame(d = t_y18, directed = TRUE)
E(tot18)$weight <- t_y18[[y18]]
is_directed(tot18) 
length(E(tot18)) == length(E(tot18)$weight)
length(unique(V(tot18)$name)) == gorder(tot18)  
is.character(V(tot18)$name) 
any(is.na(E(tot18)$weight))      
any(!is.finite(E(tot18)$weight))
length(unique(V(tot18)$name))
tot18 <- attify(tot18, att2018)
vertex_attr_names(tot18)
```

```{r}
length(unique(V(tot18)$name)) == gorder(tot18) 
is.character(V(tot18)$name) 
length(unique(att2018$iso_o)) == length(unique(V(tot18)$name))
ITNcp18 <-core_periphery_weighted(tot18,"directed")
class(ITNcp18[[2]])
cp18 <- ITNcp18[[2]]
```

```{r}
merged18 <- merge(cp18, att2018, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged18 <- subset(merged18, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged18 <- merged18 %>% rename(iso_o = id)
merged18 <- merged18 %>% rename(sigma_cp = sigma_all)
merged18 <- merged18 %>% rename(rank_cp = RANK)
merged18 <- merged18 %>% rename(cp = all_cp)
merged18 <- merged18 %>% rename(country = country_x)
```

# 2019
```{r}
y19 <- "X2019"   
t_y19 <- t[, c("iso_o", "iso_d", y19)]
t_y19 <- subset(t_y19, t_y19[[y19]] > 0)
att2019 <- read.csv("../data/cleaned/attribute2019.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot19 <- graph_from_data_frame(d = t_y19, directed = TRUE)
E(tot19)$weight <- t_y19[[y19]]
is_directed(tot19) 
length(E(tot19)) == length(E(tot19)$weight)
length(unique(V(tot19)$name)) == gorder(tot19)  
is.character(V(tot19)$name) 
any(is.na(E(tot19)$weight))      
any(!is.finite(E(tot19)$weight)) 
length(unique(V(tot19)$name))
tot19 <- attify(tot19, att2019)
vertex_attr_names(tot19)
```
```{r}
length(unique(V(tot19)$name)) == gorder(tot19) 
is.character(V(tot19)$name) 
length(unique(att2019$iso_o)) == length(unique(V(tot19)$name))
ITNcp19 <-core_periphery_weighted(tot19,"directed")
class(ITNcp19[[2]])
cp19 <- ITNcp19[[2]]
```
```{r}
merged19 <- merge(cp19, att2019, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged19 <- subset(merged19, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged19 <- merged19 %>% rename(iso_o = id)
merged19 <- merged19 %>% rename(sigma_cp = sigma_all)
merged19 <- merged19 %>% rename(rank_cp = RANK)
merged19 <- merged19 %>% rename(cp = all_cp)
merged19 <- merged19 %>% rename(country = country_x)
```

# 2020
```{r}
y20 <- "X2020"   
t_y20 <- t[, c("iso_o", "iso_d", y20)]
t_y20 <- subset(t_y20, t_y20[[y20]] > 0)
att2020 <- read.csv("../data/cleaned/attribute2020.csv", header = TRUE, as.is = TRUE, stringsAsFactors = FALSE)
tot20 <- graph_from_data_frame(d = t_y20, directed = TRUE)
E(tot20)$weight <- t_y20[[y20]]
is_directed(tot20) 
length(E(tot20)) == length(E(tot20)$weight)
length(unique(V(tot20)$name)) == gorder(tot20)  
is.character(V(tot20)$name) 
any(is.na(E(tot20)$weight))     
any(!is.finite(E(tot20)$weight)) 
length(unique(V(tot20)$name))
tot20 <- attify(tot20, att2020)
vertex_attr_names(tot20)
```
```{r}
length(unique(V(tot20)$name)) == gorder(tot20) 
is.character(V(tot20)$name) 
length(unique(att2020$iso_o)) == length(unique(V(tot20)$name))
ITNcp20 <-core_periphery_weighted(tot20,"directed")
class(ITNcp20[[2]])
cp20 <- ITNcp20[[2]]
```
```{r}
merged20 <- merge(cp20, att2020, by.x = "id", by.y = "iso_o", all.x = TRUE)
merged20 <- subset(merged20, select = -c(sigma_in, sigma_out, RANKout, RANKin, in_cp, out_cp, country_y))
# renaming 
merged20 <- merged20 %>% rename(iso_o = id)
merged20 <- merged20 %>% rename(sigma_cp = sigma_all)
merged20 <- merged20 %>% rename(rank_cp = RANK)
merged20 <- merged20 %>% rename(cp = all_cp)
merged20 <- merged20 %>% rename(country = country_x)
```


```{r}
colnames(merged00) == colnames(merged01) 
colnames(merged01) == colnames(merged02)
colnames(merged02) == colnames(merged03)
colnames(merged03) == colnames(merged04)
colnames(merged05) == colnames(merged06)
colnames(merged06) == colnames(merged07) 
colnames(merged07) == colnames(merged08)
colnames(merged08) == colnames(merged09)
colnames(merged10) == colnames(merged11)
colnames(merged11) == colnames(merged12)
colnames(merged12) == colnames(merged13) 
colnames(merged13) == colnames(merged14)
colnames(merged14) == colnames(merged15)
colnames(merged15) == colnames(merged16)
colnames(merged16) == colnames(merged17)
colnames(merged17) == colnames(merged18)
colnames(merged18) == colnames(merged19)
colnames(merged19) == colnames(merged20)
```

```{r}
write.csv(merged00, "../data/cleaned/attribute2000.csv")
write.csv(merged01, "../data/cleaned/attribute2001.csv")
write.csv(merged02, "../data/cleaned/attribute2002.csv")
write.csv(merged03, "../data/cleaned/attribute2003.csv")
write.csv(merged04, "../data/cleaned/attribute2004.csv")
write.csv(merged05, "../data/cleaned/attribute2005.csv")
write.csv(merged06, "../data/cleaned/attribute2006.csv")
write.csv(merged07, "../data/cleaned/attribute2007.csv")
write.csv(merged08, "../data/cleaned/attribute2008.csv")
write.csv(merged09, "../data/cleaned/attribute2009.csv")
write.csv(merged10, "../data/cleaned/attribute2010.csv")
write.csv(merged11, "../data/cleaned/attribute2011.csv")
write.csv(merged12, "../data/cleaned/attribute2012.csv")
write.csv(merged13, "../data/cleaned/attribute2013.csv")
write.csv(merged14, "../data/cleaned/attribute2014.csv")
write.csv(merged15, "../data/cleaned/attribute2015.csv")
write.csv(merged16, "../data/cleaned/attribute2016.csv")
write.csv(merged17, "../data/cleaned/attribute2017.csv")
write.csv(merged18, "../data/cleaned/attribute2018.csv")
write.csv(merged19, "../data/cleaned/attribute2019.csv")
write.csv(merged20, "../data/cleaned/attribute2020.csv")
```

